---
title: "Stress Related to COVID19 on Healthcare Workers -- ML Analysis"
subtitle: "By: GSRC, MACL, GJAR for the Bio-Math Group (UABC, UANL, UPP)"
output: html_document
bibliography: references.bib
csl: apa.csl
---

## Data Quality Report as a preliminary exploration

Since the data is recorded in qualitative scales, the following report is generated based on the [guidelines](https://drive.google.com/file/d/0B0fVQlRpn_q6WE10Q3otZXAyUk0/view?usp=sharing) proposed by @kelleher2020fundamentals.
```{r echo=FALSE, message=FALSE, warning=FALSE}
source("Functions/QOfCategoricalF.R")
datar <- read.csv(file = "Data/datosNum.csv", header = TRUE, sep = ",")
datar <- na.omit(datar)
dqr <- QOfCategoricalF(datar[,2:37])
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
library(tibble)

dqr <- add_column(dqr, variable = names(datar[,2:37]), .before = "Count")

dqr %>%
  kbl() %>%
  kable_material("hover", full_width = F)
library(psych)
```

# Ward Hierarchical Clustering with Bootstrapped p-Values


**Result for Chronbach´s Alpha was: `r round(psych::alpha(datar, check.keys = TRUE)$total$std.alpha,3)`**
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11, fig.height = 12}
#library(psych)
#psych::alpha(datar, check.keys = TRUE)$total$std.alpha


# Ward Hierarchical Clustering with Bootstrapped p values #El buenas buenas!!!!!
library(pvclust)

#fit <- pvclust(datar, method.hclust="ward",
fit <- pvclust(datar[,2:37], method.hclust="ward.D",
               method.dist="euclidean")
plot(fit) # dendogram with p values
# add rectangles around groups highly supported by the data
pvrect(fit, alpha=.95)
```


## Distribution by specific variables

### Level of Stress
```{r echo=FALSE, message=FALSE, warning=FALSE}
# An?lisis y ?rbol
library(C50)
library(ggplot2)
library(plotly)

dataC <- read.csv(file = "Data/class.csv", header = TRUE, sep = ",")
attach(dataC)

dataC <- as.data.frame(dataC)
countsStress = table(dataC$Class)
#barplot(countsStress, main="Stress  Distribution in Healthcare Personnel",
#        xlab="Stress Level", ylab="Frequency") 
plot_ly(type = "histogram",
        x = dataC$Class) %>%
  layout(title = "Distribution of Level of Stress by Profession")
```

### Distribution by Profession
```{r echo=FALSE, message=FALSE, warning=FALSE}
plot_ly(type = "histogram",
        x = dataC$Prof) %>%
  layout(title = "Distribution by Profession")

```

## Distribution by Area of Work
```{r echo=FALSE, message=FALSE, warning=FALSE}
plot_ly(type = "histogram",
        x = dataC$area) %>%
  layout(title = "Distribution by Area of Work")


```


## Decision Tree

The algorithm used to implement the Decision Tree was [C50](http://www.socr.umich.edu/people/dinov/courses/DSPA_notes/08_DecisionTreeClass.html)
```{r echo=FALSE, fig.width= 20, fig.height=9, message=FALSE, warning=FALSE}
#http://mercury.webster.edu/aleshunas/R_learning_infrastructure/Classification%20of%20data%20using%20decision%20tree%20and%20regression%20tree%20methods.html
modelo.arbol <-C5.0(Class~Prof+area+Dan.Con+Socio+Xeno+Trauma+Comp, data=dataC)
plot(modelo.arbol, main = "Resulting Decision Tree") 

#summary(modelo.arbol)
```





## References